---
title: "Split-sample sims"
output:
  github_document
---

In these simulations, I consider a set of different synthetic estimators. When $\theta_0$ is specified, it is the DR. Leacy and Stuart is used throughout. The synthetic estimators are as follows:

- *Old*: this is the original way we have always done things, using raw differences: $\hat{\Delta} = \hat{\theta}_i - \hat{\theta}_0$. 
- *Shrunk*: this uses the raw differences but scales them by $n$: $\hat{\Delta} = n^{-1}(\hat{\theta}_i - \hat{\theta}_0)$.
- *Null*: this is the so-called tree-based method we've been using, where we remove the estimated treatment effect (according to causal forest) and then bootstrap, and compare to a null ATE.
- *Hybrid_gn*: this uses the typical bootstrap, but the bias is estimated by comparing to the causal forest ATE.

We also compare to the four candidate estimators: DR, regression, IPW, and stratifying on the PS. And we compare to the causal forest estimator, even though it's not part of the composite. 

Finally, we consider multiple split-sample approaches. The number following the synthetic estimator indicates the number of splits used to estimate it. A zero indicates that no splits were used - standard synthetic estimator. A one indicates the original split-sample approach, where we fit on two halves. A ten indicates that we repeat the split-sample (and fit on each half) ten times. 

# Leacy and Stuart results

Note: I used a log-scale on these results to make clear the differences between the best approaches.

```{r echo = FALSE, message = FALSE, warning = FALSE, fig.width = 8, fig.height = 8}
library(tidyverse)
library(here)
library(glue)
library(knitr)
library(magrittr)

sim_parameters <- expand.grid(
  run = 1:500,
  j = 1:4,
  n = c(500, 2000),
  d = c('ls')
)
sim_parameters %<>%
  mutate(sim = as.character(1:nrow(sim_parameters)))

all_sims <- readRDS(here(glue('results/comparison_sim_ls.rds')))
theta1 <- map(all_sims, 'all_thetas') %>%
        bind_rows(.id = 'sim') %>%
  inner_join(sim_parameters) %>%
  mutate(j_d = case_when(j == 1 ~ 'Both correct',
                         j == 2 ~ 'PS model correct',
                         j == 3 ~ 'Outcome model correct',
                         j == 4 ~ 'Both models wrong'),
         estimator = paste0(type, '-', splits))
mse_res <- theta1 %>%
        group_by(j_d, n, d, estimator) %>%
        summarise(mse = mean((ate + 0.4)^2),
                  bias = mean(ate + 0.4),
                  var = var(ate))
      
      ggplot(mse_res, aes(x = estimator, y = mse)) +
        geom_col() +
        facet_wrap(n ~ j_d, scales = 'free_x') +
        theme_bw() +
        coord_flip() +
        ggtitle('MSE') +
        scale_y_log10()
      
      ggplot(mse_res, aes(x = estimator, y = bias)) +
        geom_col() +
        facet_wrap(n ~ j_d, scales = 'free_x') +
        theme_bw() +
        coord_flip() +
        ggtitle('Bias') +
        scale_y_log10()

kable(mse_res %>% arrange(n, mse))

```

### Comparing the coefficients

```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.height = 8, fig.width = 8}
b1 <- map(all_sims, 'all_bs') %>%
        bind_rows(.id = 'sim') %>%
  filter(type != 'raw') %>%
  inner_join(sim_parameters) %>%
  mutate(j_d = case_when(j == 1 ~ 'Both correct',
                         j == 2 ~ 'PS model correct',
                         j == 3 ~ 'Outcome model correct',
                         j == 4 ~ 'Both models wrong'),
         estimator = paste0(type, '-', splits))
b_sum <- b1 %>%
        group_by(j_d, n, d, est, estimator) %>%
        summarise(bhat = mean(b),
                  bvar = var(b),
                  b_se = sd(b))
      print(ggplot(b_sum, 
                   aes(x = est, y = bhat, 
                       group = estimator, fill = estimator)) +
        geom_col(position = 'dodge') +
        facet_grid(n ~ j_d))
      
      print(ggplot(b_sum, aes(x = n, y = b_se, group = est, fill = est)) +
        geom_col(position = 'dodge') +
        facet_grid(estimator ~ j_d) +
          scale_y_sqrt())
      


kable(b_sum %>% arrange( j_d, estimator, est, n))
```
